### 2018-12-04 Sections/physical_architectures_for_quantum_computing.tex
indexing

Originally it was believed that universal optical quantum computation, specifically the implementation of 2-qubit entangling gates (such as CNOT or CZ gates), would require extremely (and unrealistically) strong optical non-linearities that implement a non-linear sign-shift (NS) gate,
\begin{align} \label{eq:NS_trans}\index{Non-linear sign-shift (NS) gate}
NS: \alpha\ket{0}+\beta\ket{1}+\gamma\ket{2}\to\alpha\ket{0}+\beta\ket{1}-\gamma\ket{2},
\end{align}
in the photon-number basis, up to normalisation (which is determined by the post-selection success probability). That is, it applies a $\pi$ phase-shift to only the $\ket{2}$ component of a photon-number superposition. The breakthrough result by KLM demonstrated that this is in fact not the case at all. Instead, the NS gate can be implemented non-deterministically using post-selected linear optics. Two such NS gates allow the construction of a single CZ gate. The construction of the KLM NS and CZ gates are shown in Figs.~\ref{fig:KLM_gate} \& \ref{fig:KLM_explain}. Equivalently, a CNOT gate may be trivially constructed via conjugation by Hadamard gates, based on the identity \mbox{$\hat{H}\hat{Z}\hat{H}=\hat{X}$}.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.42\textwidth]{KLM_gate}
\captionspacefig \caption{(a) A KLM CZ gate, employing dual-rail encoding, constructed from two non-linear sign-shift (NS) gates, which apply a $\pi$ phase-shift to only $\ket{2}$ terms in the photon-number basis. (b) Construction of the non-deterministic linear optics NS gate. Two ancillary states -- one $\ket{1}$ and one $\ket{0}$ -- are employed, and two photo-detectors post-select upon detecting $\ket{1}\bra{1}$ and $\ket{0}\bra{0}$ respectively. The beamsplitter reflectivities in (a) are 50:50, and in (b) chosen such that the amplitudes obey Eq.~(\ref{eq:NS_trans}).}. \label{fig:KLM_gate} \index{Knill-Laflamme-Milburn (KLM)}\index{Non-linear sign-shift (NS) gate}
\end{figure}

@@

It was then noted \cite{BrowneRudolph} that CZ gates aren't required at all for the preparation of optical cluster states. Instead, parity measurements (Sec.~\ref{sec:bell_proj})\index{Bell measurements} operating in a rotated basis may be used to fuse smaller cluster states into larger ones, albeit acting destructively on two of the qubits, and also being non-deterministic, with a success probability of $1/2$. These gates have become known as \textit{fusion gates}, of which there are two types:
\begin{itemize}
	\item Type-I: destroy only a single photon, but require efficient number-resolved detection.
	\item Type-II: destroy two photons, but only require on/off detectors, since the gate succeeds upon coincidence events only and preserves photon-number.
\end{itemize}
Both types of gates have several highly favourable characteristics:
\begin{itemize}
	\item Unlike the KLM CZ gate, only HOM stability is required (Sec.~\ref{sec:opt_stab}). At no stage in the cluster state preparation procedure is any interferometric (i.e wavelength-scale) stability required.
	\item Gate failure is heralded by measurement of the wrong photon-number.
	\item Gate failure measures the respective qubits in the computational basis, thereby simply removing those qubits from the cluster state graph, whilst preserving the remainder of the state, which can be `recycled'\index{Cluster states!Recycling} for reuse.
\end{itemize}

@@

One of the key outcomes was that a \textsc{Balanced} strategy\index{Balanced strategy} is optimal in terms of preparation rate. This is simply a strategy which preferentially always bonds clusters of equal length, beginning with the largest ones available. Asymmetric strategies, which bond clusters of differing lengths were found to be far less efficient.

@@

\paragraph{Lattice clusters}\index{Lattice cluster states}

@@

\paragraph{On-demand cluster state preparation}\index{On-demand cluster state preparation}

@@

The key ingredient here is the cross-Kerr interaction\index{Cross-Kerr Interaction}, which obeys the Hamiltonian,
\begin{align}
\hat{H}_\mathrm{ck} = \hbar \chi \hat{n}_a \hat{n}_b,	
\end{align}
where \mbox{$\hat{n}_a = \hat{a}^\dag \hat{a}$} and \mbox{$\hat{n}_b = \hat{b}^\dag \hat{b}$} are the photon-number operators\index{Photon-number operators} for modes $a$ and $b$ respectively, and $\chi$ is the interaction strength\index{Interaction strength}, which is typically very small in the lab. This Hamiltonian generates the unitary transformation,
\begin{align}
\hat{U}_\mathrm{ck} = e^{i\theta\hat{n}_a\hat{n}_b}.
\end{align}
The magnitude of the induced phase-shift is now proportional to photon-number and,  
\begin{align}
\theta = \chi t,	
\end{align}
where $t$ is the interaction time\index{Interaction time}. For strongly entangling gates we need \mbox{$\theta \approx \pi$}.

@@

\begin{figure*}[!htpb]
	\includegraphics[clip=true, width=\textwidth]{weak_ck_parity_gate}
\captionspacefig \caption{Construction of a two-mode, polarisation-encoded, photonic parity gate using an ancillary qubus coherent state $\ket\alpha$, mediating entangling photonic interactions between $\ket{\psi_a}$ and $\ket{\psi_b}$ via weak cross-Kerr non-linearities (denoted by the controlled-$\theta$ gates). The polarising beamsplitters\index{Polarising beamsplitters} are used to switch between polarisation and dual-rail encoding. The qubus is an optical channel, potentially across long distances over the quantum internet for performing distributed gates. The measurement $M$ is a homodyne measurement\index{Homodyne measurements}, which feedforwards an $X$-quadrature measurement outcome to a local phase correction. This gate could be used for preparing distributed photonic cluster states, a resource for universal quantum computation.}\label{fig:weak_ck_parity}	
\end{figure*}

Consider the parity measurement circuit shown in Fig.~\ref{fig:weak_ck_parity}. Let us begin with two polarisation-encoded photonic qubits, which might be separated over long distances, and a coherent state in the shared qubus mode,
\begin{align}
\ket{\psi_\mathrm{in}} &= (\alpha_{HH} \ket{H}\ket{H} + \alpha_{HV} \ket{H}\ket{V} \nonumber\\
&+\alpha_{VH} \ket{V}\ket{H} + \alpha_{VV} \ket{V}\ket{V})\ket\alpha.
\end{align}
Applying the cross-Kerr interactions leaves us in the state,
\begin{align}
\hat{U}_\mathrm{gate} \ket{\psi_\mathrm{in}} &= [\alpha_{HH} \ket{H}\ket{H}] + \alpha_{VV} \ket{V}\ket{V}]\ket\alpha \nonumber\\
	&+ \alpha_{HV} \ket{H}\ket{V}\ket{\alpha e^{i\theta}}\nonumber\\
	&+ \alpha_{VH} \ket{V}\ket{H}\ket{\alpha e^{-i\theta}}.
\end{align}
Now the qubus state is in some superposition of $\ket\alpha$, $\ket{\alpha e^{i\theta}}$ and $\ket{\alpha e^{-i\theta}}$. The key observation is that these three coherent basis states become highly distinguishable for large $|\alpha|$ with non-zero $\theta$. Specifically, a homodyne measurement on the qubus that projects onto \mbox{$x=0$}, approximately leaves us in the state,
\begin{align}
	\ket{\psi_\mathrm{out}} = \alpha_{HH}\ket{H}\ket{H} + \alpha_{VV}\ket{V}\ket{V},
\end{align}
which corresponds to a maximally-entangling parity or Bell projection\index{Bell!Measurement}.

@@

A linear optics network acting on a tensor product of coherent state inputs implements simple matrix multiplication\index{Matrix multiplication} on the vector of coherent amplitudes. Specifically, Eq.~(\ref{eq:LO_unitary_map}) implies that for the input multi-mode coherent state,
\begin{align}
\ket{\psi}_\mathrm{in} = \ket{\vec\alpha} = \ket{\alpha_1,\dots,\alpha_m},
\end{align}
where $\alpha_i$ is the coherent amplitude of the $i$th mode, the linear map now takes the form,
\begin{align}
\beta_i = \sum_{j=1}^m U_{i,j} \alpha_j,
\end{align}
where the output state is the separable multi-mode coherent state,
\begin{align}
\ket{\psi}_\mathrm{out} = \ket{\vec\beta} = \ket{\beta_1,\dots,\beta_m}.
\end{align}
Equivalently, this could simply be expressed as the matrix equation,
\begin{align}\label{eq:coherent_state_LO_map}
\vec{\beta} = U\cdot\vec{\alpha}.
\end{align}

Of course this is not strictly a \textit{quantum} computation, since:
\begin{itemize}
\item It can be efficiently classically computed using $O(m^2)$ operations\footnote{Using the na\"ive element-wise approach, which can be further improved upon using more sophisticated contemporary algorithms.}, thus residing in \textbf{P}\index{P}.
\item Coherent states are considered classical states (i.e approximated by laser light\index{Laser light}) with strictly positive Wigner and $P$-functions\index{Wigner function}\index{P-function}.
\item There is no entanglement between modes.
\item The algorithm offers no quantum (exponential) speedup.
\end{itemize}

@@

Until now we have focussed on optical systems where quantum information is encoded into discrete variables\index{Discrete-ance variables}, such as photon-number or polarisation. However, quantum states of light can also be considered in terms of continuous-variables (CVs)\index{Continuous-variables} in phase-space\index{Phase-space}.

@@

Mathematically, there are two operators of interest, the single- and two-mode squeezing operators\index{Squeezing operators},
\begin{align}\label{eq:sq_op}
\hat{S}_\mathrm{single}(\xi) &= \exp\left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],\nonumber\\
\hat{S}_\mathrm{two}(\xi) &= \exp\left[ \xi\hat{a}_1^\dag\hat{a}_2^\dag + \xi^*\hat{a}_1\hat{a}_2 \right],
\end{align}
where \mbox{$\xi\in \mathbb{C}$} is the squeezing parameter. Both of these may be realised physically using non-linear crystals\index{Non-linear crystals} with second order non-linearities\index{Second order non-linearities}, readily available in present-day labs.

@@

\subsubsection{Bell pairs}\index{Bell states}\label{sec:CV_bell_pairs}\index{Continuous-variables!Bell states}

@@

Using a 50:50 beamsplitter to implement the reverse of Bell pair preparation, one can construct a Bell analyser for performing projections in the Bell basis\index{Bell measurements}, gifting us a highly-cherished entangling operation, useful for all manner of protocols (Part.~\ref{part:protocols}).

@@

Having demonstrated an equivalent single-mode teleporter, we have all we need to construct arbitrary measurement-based quantum computations using the generalised CZ gates as the primitive entangling operation\index{Entangling operation} for preparation of the substrate graph state.

The addition of any non-Gaussian projective measurement allows universal quantum computation using CV cluster states. A class of such gates is the non-linear phase gate\index{Non-linear phase gate},
\begin{align}
	\hat{U}_\mathrm{NL}=\exp(it\hat x^{n}),
\end{align}
where \mbox{$n\geq 3$} (the cubic phase gate\index{Cubic phase gate}).

@@

The natural example is matter qubits which couple to single-photon states, whereupon which-path erasure between coupled optical modes teleports entanglement onto the physical matter qubits\index{Entanglement!Teleportation}.\index{Which-path erasure} Similarly, measurement of the matter qubits may be performed by stimulating the emission\index{Stimulated emission} of photons from them. This idea has been applied to $\lambda$-configuration atomic qubits\index{Atomic qubits}\index{$\lambda$-configuration systems} \cite{bib:BarrettKok05}, shown in Fig.~\ref{fig:barrett_kok}, and atomic ensemble qubits \cite{bib:RohdeAtEns10} (Sec.~\ref{sec:atomic_ens}). The protocol is described in Alg.~\ref{alg:which_path}.

@@

Optically-mediated atomic ensemble architectures are particularly attractive, as discussed in Sec.~\ref{sec:atomic_ens}\index{Atomic ensembles}, owing to their long coherence lifetimes\index{Coherence time}, room temperature operation\index{Room temperature operation}, strong light-matter coupling, and robustness against qubit loss\index{Qubit loss}.

@@

One of the most widely used types of artificial atom are superconducting qubits \cite{bib:martinis1985energy, bib:shnirman1997quantum, bib:averin1998adiabatic, bib:devoret2004superconducting, bib:makhlin2001quantum}\index{Superconductors!Qubits}, a class of non-linear quantum circuits\index{Non-linear quantum circuits}. An LC oscillator\index{LC oscillator} composed of an inductor $L$\index{Inductors} and capacitance $C$\index{Capacitors} is a typical example of a linear quantum circuit\index{Linear quantum circuits} with equal spacing. By introducing a Josephson junction\index{Josephson junction} into the linear quantum circuit we can make it non-linear, with anharmonic energy spectrum.

A Josephson junction \cite{bib:josephson1974the} comprises two bulk superconducting materials\index{Superconductors}, separated by a thin layer of insulating material\index{Insulators}. In the superconducting phase the superconductors contain Cooper-pairs\index{Cooper-pairs}, composed of paired electrons. These Cooper-pairs move from one superconducting layer to another through the insulating layer via quantum tunnelling\index{Tunnelling}. The quantum mechanical nature of Josephson junctions is determined by two important energy scales:
\begin{itemize}
\item Josephson coupling energy, $E_{J}$.\index{Josephson coupling energy}
\item Coulomb energy, $E_C$.\index{Coulomb energy}
\end{itemize}
The ratio between these two energy scales determines the energy spectrum of the superconducting qubit. This yields three distinct types of qubits:
\begin{itemize}
\item Voltage-driven charge qubits \cite{bib:bouchiat1998quantum, bib:nakamura1999coherent}.\index{Charge qubits}
	\item Flux-driven flux qubits \cite{bib:friedman2000quantum, bib:van2000quantum}.\index{Flux qubits}
	\item Current-driven phase qubits \cite{bib:martinis2002rabi}.\index{Phase qubits}
\end{itemize} 
These circuits and energy level diagrams for these are illustrated in Fig.~\ref{fig:superconductor_circuits}.

@@

\subsubsection{Charge qubits}\index{Charge qubits}

A non-linear quantum circuit driven by voltage\index{Voltage} is referred to as a charge qubit, whose Hamiltonian takes the form,
\begin{align}
\hat{H} = \frac{\hat{q}^{2}}{2C} - E_{J} \cos \left( \frac{2e}{\hbar} \hat\phi \right).
\label{circuitHamiltonian}
\end{align}
Here $\hat{q}$ is the charge in the superconducting system and $\hat\phi$ is flux\index{Flux}. The total capacitance of the circuit is given by $C$, and $E_{J}$ is the Josephson energy\index{Josephson energy}. The Hamiltonian in Eq.~(\ref{circuitHamiltonian}) can be rewritten as,
\begin{align}\label{eq:charge_qubit_hamiltonian}
\hat{H} = 4E_C (\hat{n} - n_{g})^{2} - E_{J} \cos (\hat{\phi}) .
\end{align}
The variables $\hat{q}$ and $\hat{\phi}$ are canonically conjugate\index{Canonically conjugate} and satisfy the commutation relation,
\begin{align}
[ \hat{\phi},\hat{q} ] = i \hbar.
\end{align}
In a truncated charge basis the Hamiltonian is,
\begin{align}
\hat{H} &= 4 E_C \sum_{n = -N}^{N} (\hat{n} - n_{g})^{2} \ket{n}\bra{n}\nonumber\\
&- E_{J} \sum_{n = -N}^{N-1} \ket{n+1}\bra{n} + \ket{n}\bra{n+1}.
\end{align}

The energy eigenstates are the charge states\index{Charge states} $\ket{n}$, hence these qubits are referred to as charge qubits. In general the charge qubit \cite{bib:bouchiat1998quantum, bib:nakamura1999coherent} is operated in the region,
\begin{align}
	\frac{E_J}{E_C} \approx 1.
\end{align}

@@

\subsubsection{Flux qubits}\index{Flux qubits}

@@

The second class of quantum gates is built up of superconducting qubits with fixed frequencies, driven by microwaves. The cross-resonance gate\index{Cross-resonance gate}, the bSWAP\index{bSWAP gate} or Bell pairRabi gate\index{Bell pairRabi gate}, and the MAP gate\index{MAP gate} belong to this class. The effective Hamiltonian of the cross-resonance gate is,
\begin{align}
\hat{H}_\mathrm{eff} = - \left( \frac{\tilde{\omega}_{1} - \tilde{\omega}_2}{2} \right) \hat\sigma_{z,1} + \frac{\Omega(t)}{2} \left(\hat\sigma_{x,1} - \frac{J}{\Delta_{12}} \hat\sigma_{z,1} \hat\sigma_{x,2} \right),
\end{align}
where,
\begin{align}
	\tilde{\omega}_{1} &= \omega_{1} + \frac{J^{2}}{\Delta_{12}}, \nonumber\\
		\tilde{\omega}_{2} &= \omega_{2} - \frac{J^{2}}{\Delta_{12}}, \nonumber\\
\Delta &= \omega_{1} -\omega_{2}.		
\end{align}
The factors $\omega_{1}$ and $\omega_{2}$ are the frequencies of the first and second qubits, and $\Delta_{12}$ is the detuning\index{Detuning}. The first qubit is rotating with frequency $\frac{1}{2}(\tilde{\omega_{1}} - \tilde{\omega_{2}})$ around the $Z$-axis, with a little shift in the $X$-direction, yielding an $X$-gate. Similarly we can construct a microwave-activated CZ (MAP) gate\index{MAP gate} using two transmons. The system of two transmons is modelled using a system of two coupled Duffing oscillators\index{Duffing oscillators}. The effective Hamiltonian in the two qubit space reads,
\begin{align}
\hat{H}_\mathrm{eff} &= - \frac{1}{2} \left( \omega_{01} - \frac{\zeta}{2} \right) \hat\sigma_{z,1} - \frac{1}{2} \left( \omega_{10} - \frac{\zeta}{2} \right) \hat\sigma_{z,2} \nonumber\\
&+ \frac{\zeta}{4} \hat\sigma_{z,1} \hat\sigma_{z,2}. 
\end{align}

>>>>

Originally it was believed that universal optical quantum computation, specifically the implementation of 2-qubit entangling gates (such as CNOT or CZ gates), would require extremely (and unrealistically) strong optical non-linearities that implement a non-linear sign-shift (NS) gate,
\begin{align} \label{eq:NS_trans}\index{Non-linear!Sign-shift (NS) gate}
NS: \alpha\ket{0}+\beta\ket{1}+\gamma\ket{2}\to\alpha\ket{0}+\beta\ket{1}-\gamma\ket{2},
\end{align}
in the photon-number basis, up to normalisation (which is determined by the post-selection success probability). That is, it applies a $\pi$ phase-shift to only the $\ket{2}$ component of a photon-number superposition. The breakthrough result by KLM demonstrated that this is in fact not the case at all. Instead, the NS gate can be implemented non-deterministically using post-selected linear optics. Two such NS gates allow the construction of a single CZ gate. The construction of the KLM NS and CZ gates are shown in Figs.~\ref{fig:KLM_gate} \& \ref{fig:KLM_explain}. Equivalently, a CNOT gate may be trivially constructed via conjugation by Hadamard gates, based on the identity \mbox{$\hat{H}\hat{Z}\hat{H}=\hat{X}$}.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.42\textwidth]{KLM_gate}
\captionspacefig \caption{(a) A KLM CZ gate, employing dual-rail encoding, constructed from two non-linear sign-shift (NS) gates, which apply a $\pi$ phase-shift to only $\ket{2}$ terms in the photon-number basis. (b) Construction of the non-deterministic linear optics NS gate. Two ancillary states -- one $\ket{1}$ and one $\ket{0}$ -- are employed, and two photo-detectors post-select upon detecting $\ket{1}\bra{1}$ and $\ket{0}\bra{0}$ respectively. The beamsplitter reflectivities in (a) are 50:50, and in (b) chosen such that the amplitudes obey Eq.~(\ref{eq:NS_trans}).}. \label{fig:KLM_gate} \index{Knill-Laflamme-Milburn (KLM)}\index{Non-linear!Sign-shift (NS) gate}
\end{figure}

@@

It was then noted \cite{BrowneRudolph} that CZ gates aren't required at all for the preparation of optical cluster states. Instead, parity measurements (Sec.~\ref{sec:bell_proj})\index{Bell!Measurements} operating in a rotated basis may be used to fuse smaller cluster states into larger ones, albeit acting destructively on two of the qubits, and also being non-deterministic, with a success probability of $1/2$. These gates have become known as \textit{fusion gates}, of which there are two types:
\begin{itemize}
	\item Type-I: destroy only a single photon, but require efficient number-resolved detection.
	\item Type-II: destroy two photons, but only require on/off detectors, since the gate succeeds upon coincidence events only and preserves photon-number.
\end{itemize}
Both types of gates have several highly favourable characteristics:
\begin{itemize}
	\item Unlike the KLM CZ gate, only HOM stability is required (Sec.~\ref{sec:opt_stab}). At no stage in the cluster state preparation procedure is any interferometric (i.e wavelength-scale) stability required.
	\item Gate failure is heralded by measurement of the wrong photon-number.
	\item Gate failure measures the respective qubits in the computational basis, thereby simply removing those qubits from the cluster state graph, whilst preserving the remainder of the state, which can be `recycled'\index{Cluster states!Recycling} for reuse.
\end{itemize}

@@

One of the key outcomes was that a \textsc{Balanced} strategy\index{Balanced!Strategy} is optimal in terms of preparation rate. This is simply a strategy which preferentially always bonds clusters of equal length, beginning with the largest ones available. Asymmetric strategies, which bond clusters of differing lengths were found to be far less efficient.

@@

\paragraph{Lattice clusters}\index{Lattice!Cluster states}

@@

\paragraph{On-demand cluster state preparation}\index{On-demand!Cluster state preparation}

@@

The key ingredient here is the cross-Kerr interaction\index{Cross-Kerr Interaction}, which obeys the Hamiltonian,
\begin{align}
\hat{H}_\mathrm{ck} = \hbar \chi \hat{n}_a \hat{n}_b,	
\end{align}
where \mbox{$\hat{n}_a = \hat{a}^\dag \hat{a}$} and \mbox{$\hat{n}_b = \hat{b}^\dag \hat{b}$} are the photon-number operators\index{Photon-number operators} for modes $a$ and $b$ respectively, and $\chi$ is the interaction strength\index{Interaction!Strength}, which is typically very small in the lab. This Hamiltonian generates the unitary transformation,
\begin{align}
\hat{U}_\mathrm{ck} = e^{i\theta\hat{n}_a\hat{n}_b}.
\end{align}
The magnitude of the induced phase-shift is now proportional to photon-number and,  
\begin{align}
\theta = \chi t,	
\end{align}
where $t$ is the interaction time\index{Interaction!Time}. For strongly entangling gates we need \mbox{$\theta \approx \pi$}.

@@

\begin{figure*}[!htpb]
	\includegraphics[clip=true, width=\textwidth]{weak_ck_parity_gate}
\captionspacefig \caption{Construction of a two-mode, polarisation-encoded, photonic parity gate using an ancillary qubus coherent state $\ket\alpha$, mediating entangling photonic interactions between $\ket{\psi_a}$ and $\ket{\psi_b}$ via weak cross-Kerr non-linearities (denoted by the controlled-$\theta$ gates). The polarising beamsplitters\index{Polarising beamsplitters} are used to switch between polarisation and dual-rail encoding. The qubus is an optical channel, potentially across long distances over the quantum internet for performing distributed gates. The measurement $M$ is a homodyne measurement\index{Homodyne detection}, which feedforwards an $X$-quadrature measurement outcome to a local phase correction. This gate could be used for preparing distributed photonic cluster states, a resource for universal quantum computation.}\label{fig:weak_ck_parity}	
\end{figure*}

Consider the parity measurement circuit shown in Fig.~\ref{fig:weak_ck_parity}. Let us begin with two polarisation-encoded photonic qubits, which might be separated over long distances, and a coherent state in the shared qubus mode,
\begin{align}
\ket{\psi_\mathrm{in}} &= (\alpha_{HH} \ket{H}\ket{H} + \alpha_{HV} \ket{H}\ket{V} \nonumber\\
&+\alpha_{VH} \ket{V}\ket{H} + \alpha_{VV} \ket{V}\ket{V})\ket\alpha.
\end{align}
Applying the cross-Kerr interactions leaves us in the state,
\begin{align}
\hat{U}_\mathrm{gate} \ket{\psi_\mathrm{in}} &= [\alpha_{HH} \ket{H}\ket{H}] + \alpha_{VV} \ket{V}\ket{V}]\ket\alpha \nonumber\\
	&+ \alpha_{HV} \ket{H}\ket{V}\ket{\alpha e^{i\theta}}\nonumber\\
	&+ \alpha_{VH} \ket{V}\ket{H}\ket{\alpha e^{-i\theta}}.
\end{align}
Now the qubus state is in some superposition of $\ket\alpha$, $\ket{\alpha e^{i\theta}}$ and $\ket{\alpha e^{-i\theta}}$. The key observation is that these three coherent basis states become highly distinguishable for large $|\alpha|$ with non-zero $\theta$. Specifically, a homodyne measurement on the qubus that projects onto \mbox{$x=0$}, approximately leaves us in the state,
\begin{align}
	\ket{\psi_\mathrm{out}} = \alpha_{HH}\ket{H}\ket{H} + \alpha_{VV}\ket{V}\ket{V},
\end{align}
which corresponds to a maximally-entangling parity or Bell projection\index{Bell!Measurements}.

@@

A linear optics network acting on a tensor product of coherent state inputs implements simple matrix multiplication\index{Matrix!Multiplication} on the vector of coherent amplitudes. Specifically, Eq.~(\ref{eq:LO_unitary_map}) implies that for the input multi-mode coherent state,
\begin{align}
\ket{\psi}_\mathrm{in} = \ket{\vec\alpha} = \ket{\alpha_1,\dots,\alpha_m},
\end{align}
where $\alpha_i$ is the coherent amplitude of the $i$th mode, the linear map now takes the form,
\begin{align}
\beta_i = \sum_{j=1}^m U_{i,j} \alpha_j,
\end{align}
where the output state is the separable multi-mode coherent state,
\begin{align}
\ket{\psi}_\mathrm{out} = \ket{\vec\beta} = \ket{\beta_1,\dots,\beta_m}.
\end{align}
Equivalently, this could simply be expressed as the matrix equation,
\begin{align}\label{eq:coherent_state_LO_map}
\vec{\beta} = U\cdot\vec{\alpha}.
\end{align}

Of course this is not strictly a \textit{quantum} computation, since:
\begin{itemize}
\item It can be efficiently classically computed using $O(m^2)$ operations\footnote{Using the na\"ive element-wise approach, which can be further improved upon using more sophisticated contemporary algorithms.}, thus residing in \textbf{P}\index{P}.
\item Coherent states are considered classical states (i.e approximated by laser light\index{Lasers!Light}) with strictly positive Wigner and $P$-functions\index{Wigner function}\index{P-function}.
\item There is no entanglement between modes.
\item The algorithm offers no quantum (exponential) speedup.
\end{itemize}

@@

Until now we have focussed on optical systems where quantum information is encoded into discrete variables\index{Discrete-variables}, such as photon-number or polarisation. However, quantum states of light can also be considered in terms of continuous-variables (CVs)\index{Continuous-variables} in phase-space\index{Phase-space}.

@@

Mathematically, there are two operators of interest, the single- and two-mode squeezing operators\index{Squeezing!Operators},
\begin{align}\label{eq:sq_op}
\hat{S}_\mathrm{single}(\xi) &= \exp\left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],\nonumber\\
\hat{S}_\mathrm{two}(\xi) &= \exp\left[ \xi\hat{a}_1^\dag\hat{a}_2^\dag + \xi^*\hat{a}_1\hat{a}_2 \right],
\end{align}
where \mbox{$\xi\in \mathbb{C}$} is the squeezing parameter. Both of these may be realised physically using non-linear crystals\index{Non-linear!Crystals} with second order non-linearities\index{Second order non-linearities}, readily available in present-day labs.

@@

\subsubsection{Bell pairs}\index{Bell!States}\label{sec:CV_bell_pairs}\index{Continuous-variables!Bell states}

@@

Using a 50:50 beamsplitter to implement the reverse of Bell pair preparation, one can construct a Bell analyser for performing projections in the Bell basis\index{Bell!Measurements}, gifting us a highly-cherished entangling operation, useful for all manner of protocols (Part.~\ref{part:protocols}).

@@

Having demonstrated an equivalent single-mode teleporter, we have all we need to construct arbitrary measurement-based quantum computations using the generalised CZ gates as the primitive entangling operation\index{Entangling operations} for preparation of the substrate graph state.

The addition of any non-Gaussian projective measurement allows universal quantum computation using CV cluster states. A class of such gates is the non-linear phase gate\index{Non-linear!Phase gate},
\begin{align}
	\hat{U}_\mathrm{NL}=\exp(it\hat x^{n}),
\end{align}
where \mbox{$n\geq 3$} (the cubic phase gate\index{Cubic phase gate}).

@@

The natural example is matter qubits which couple to single-photon states, whereupon which-path erasure between coupled optical modes teleports entanglement onto the physical matter qubits\index{Entanglement!Teleportation}.\index{Which-path erasure} Similarly, measurement of the matter qubits may be performed by stimulating the emission\index{Stimulated emission} of photons from them. This idea has been applied to $\lambda$-configuration atomic qubits\index{Atomic!Qubits}\index{$\lambda$-configuration systems} \cite{bib:BarrettKok05}, shown in Fig.~\ref{fig:barrett_kok}, and atomic ensemble qubits \cite{bib:RohdeAtEns10} (Sec.~\ref{sec:atomic_ens}). The protocol is described in Alg.~\ref{alg:which_path}.

@@

Optically-mediated atomic ensemble architectures are particularly attractive, as discussed in Sec.~\ref{sec:atomic_ens}\index{Atomic!Ensembles}, owing to their long coherence lifetimes\index{Coherence!Time}, room temperature operation\index{Room temperature operation}, strong light-matter coupling, and robustness against qubit loss\index{Qubit loss}.

@@

One of the most widely used types of artificial atom are superconducting qubits \cite{bib:martinis1985energy, bib:shnirman1997quantum, bib:averin1998adiabatic, bib:devoret2004superconducting, bib:makhlin2001quantum}\index{Superconductors!Qubits}, a class of non-linear quantum circuits\index{Non-linear!Quantum circuits}. An LC oscillator\index{LC!Oscillator} composed of an inductor $L$\index{Inductors} and capacitance $C$\index{Capacitors} is a typical example of a linear quantum circuit\index{Linear quantum circuits} with equal spacing. By introducing a Josephson junction\index{Josephson!Junction} into the linear quantum circuit we can make it non-linear, with anharmonic energy spectrum.

A Josephson junction \cite{bib:josephson1974the} comprises two bulk superconducting materials\index{Superconductors}, separated by a thin layer of insulating material\index{Insulators}. In the superconducting phase the superconductors contain Cooper-pairs\index{Cooper-pairs}, composed of paired electrons. These Cooper-pairs move from one superconducting layer to another through the insulating layer via quantum tunnelling\index{Tunnelling}. The quantum mechanical nature of Josephson junctions is determined by two important energy scales:
\begin{itemize}
\item Josephson coupling energy, $E_{J}$.\index{Josephson!Coupling energy}
\item Coulomb energy, $E_C$.\index{Coulomb!Energy}
\end{itemize}
The ratio between these two energy scales determines the energy spectrum of the superconducting qubit. This yields three distinct types of qubits:
\begin{itemize}
\item Voltage-driven charge qubits \cite{bib:bouchiat1998quantum, bib:nakamura1999coherent}.\index{Charge!Qubits}
	\item Flux-driven flux qubits \cite{bib:friedman2000quantum, bib:van2000quantum}.\index{Flux!Qubits}
	\item Current-driven phase qubits \cite{bib:martinis2002rabi}.\index{Phase qubits}
\end{itemize} 
These circuits and energy level diagrams for these are illustrated in Fig.~\ref{fig:superconductor_circuits}.

@@

\subsubsection{Charge qubits}\index{Charge!Qubits}

A non-linear quantum circuit driven by voltage\index{Voltage} is referred to as a charge qubit, whose Hamiltonian takes the form,
\begin{align}
\hat{H} = \frac{\hat{q}^{2}}{2C} - E_{J} \cos \left( \frac{2e}{\hbar} \hat\phi \right).
\label{circuitHamiltonian}
\end{align}
Here $\hat{q}$ is the charge in the superconducting system and $\hat\phi$ is flux\index{Flux}. The total capacitance of the circuit is given by $C$, and $E_{J}$ is the Josephson energy\index{Josephson!Energy}. The Hamiltonian in Eq.~(\ref{circuitHamiltonian}) can be rewritten as,
\begin{align}\label{eq:charge_qubit_hamiltonian}
\hat{H} = 4E_C (\hat{n} - n_{g})^{2} - E_{J} \cos (\hat{\phi}) .
\end{align}
The variables $\hat{q}$ and $\hat{\phi}$ are canonically conjugate\index{Canonically conjugate} and satisfy the commutation relation,
\begin{align}
[ \hat{\phi},\hat{q} ] = i \hbar.
\end{align}
In a truncated charge basis the Hamiltonian is,
\begin{align}
\hat{H} &= 4 E_C \sum_{n = -N}^{N} (\hat{n} - n_{g})^{2} \ket{n}\bra{n}\nonumber\\
&- E_{J} \sum_{n = -N}^{N-1} \ket{n+1}\bra{n} + \ket{n}\bra{n+1}.
\end{align}

The energy eigenstates are the charge states\index{Charge!States} $\ket{n}$, hence these qubits are referred to as charge qubits. In general the charge qubit \cite{bib:bouchiat1998quantum, bib:nakamura1999coherent} is operated in the region,
\begin{align}
	\frac{E_J}{E_C} \approx 1.
\end{align}

@@

\subsubsection{Flux qubits}\index{Flux!Qubits}

@@

The second class of quantum gates is built up of superconducting qubits with fixed frequencies, driven by microwaves. The cross-resonance gate\index{Cross-resonance gate}, the bSWAP\index{bSWAP gate}, and the MAP gate\index{MAP gate} belong to this class. The effective Hamiltonian of the cross-resonance gate is,
\begin{align}
\hat{H}_\mathrm{eff} = - \left( \frac{\tilde{\omega}_{1} - \tilde{\omega}_2}{2} \right) \hat\sigma_{z,1} + \frac{\Omega(t)}{2} \left(\hat\sigma_{x,1} - \frac{J}{\Delta_{12}} \hat\sigma_{z,1} \hat\sigma_{x,2} \right),
\end{align}
where,
\begin{align}
	\tilde{\omega}_{1} &= \omega_{1} + \frac{J^{2}}{\Delta_{12}}, \nonumber\\
		\tilde{\omega}_{2} &= \omega_{2} - \frac{J^{2}}{\Delta_{12}}, \nonumber\\
\Delta &= \omega_{1} -\omega_{2}.		
\end{align}
The factors $\omega_{1}$ and $\omega_{2}$ are the frequencies of the first and second qubits, and $\Delta_{12}$ is the detuning\index{Detuning}. The first qubit is rotating with frequency $\frac{1}{2}(\tilde{\omega_{1}} - \tilde{\omega_{2}})$ around the $Z$-axis, with a little shift in the $X$-direction, yielding an $X$-gate. Similarly we can construct a microwave-activated CZ (MAP) gate\index{MAP gate} using two transmons. The system of two transmons is modelled using a system of two coupled Duffing oscillators\index{Duffing oscillators}. The effective Hamiltonian in the two qubit space reads,
\begin{align}
\hat{H}_\mathrm{eff} &= - \frac{1}{2} \left( \omega_{01} - \frac{\zeta}{2} \right) \hat\sigma_{z,1} - \frac{1}{2} \left( \omega_{10} - \frac{\zeta}{2} \right) \hat\sigma_{z,2} \nonumber\\
&+ \frac{\zeta}{4} \hat\sigma_{z,1} \hat\sigma_{z,2}. 
\end{align}
